\cvsection{Work Experience}
\begin{cventries}

  \cventry
  {Full Stack Developer, Prof. Manindra Agrawal}
  {\href{https://yashsriv.org/2016/10/thoughts.html}{New York Office, IIT Kanpur}}
  {India}
  {May 2016 - Present}
  {
    \begin{cvitems}
      \item Summer Intern continued as a volunteer \& peer mentor.
      \item Worked on a scalable web application with an extensive technology
        stack using Postgres, Couchbase, Kafka, etc.
      \item	Implemented Notifications, XSRF \& XSSI Protection and batch
        processing of api requests in the backend API.
      \item Integrated ProseMirror into an existing Angular App
      \item Reimplemented an entire Angular application as per the redux
        architecture for easy extensibility and modularity.
        \ifdefined \ONEPAGE \else
      \item Technologies used: Scala with Akka, Couchbase, Angular with TypeScript, Redux
        \fi
    \end{cvitems}
  }

  \cventry
  {Summer Intern, Prof. Justin Cappos}
  {\href{https://yashsriv.org/2018/07/nyu.html}{New York University}}
  {New York City, USA}
  {May 2018 - July 2018}
  {
    \begin{cvitems}
      \item Worked on setting up an one-shot ansible project to enable
        organizations to easily set up debian package rebuilding infrastructure
        for independent verification of packages.
      \item Implemented three different microservices to orchestrate the entire
        setup and seamlessly display results via an API.
    \ifdefined\ONEPAGE
    \else
        A builder to rebuild the packages, a visualizer to expose all the
        metadata \& buildinfo and a scheduler to schedule building of packages.
        \fi
      \item Interacted with the reproducible-builds community to get feedback
        and design decisions approved.
      \item Added support for ed25519 cryptographic keys to the supply chain security
        framework - \href{https://in-toto.io/}{in-toto}.
        \ifdefined \ONEPAGE \else
      \item Technologies Used: Ansible, Python, Perl, debian build tools
        \fi
    \end{cvitems}
  }

  \cventry
  {OpenPrinting, The Linux Foundation}
  {\href{https://yashsriv.org/2017/08/gsoc.html}{Google Summer of Code}}
  {}
  {Summer 2017}
  {
    \begin{cvitems}
      \item Worked on the Common Printing Dialog Project.
      \item Allows easy integration of any new printing systems into existing
        applications implementing the interface.
      \item Helped design the DBus API and decide its usage.
      \item I worked with dbus and implemented the frontend print dialogs to the
        dbus interface in Libreoffice codebase.
        \ifdefined \ONEPAGE \else
      \item Technologies Used: DBus, C++, CUPS, Google Cloud Printing
        \fi
    \end{cvitems}
  }

\ifdefined\ONEPAGE
\else
  \cventry
  {Full Stack Developer}
  {\href{http://www.localites.com}{Localites}}
  {Freelance}
  {Dec 2018 - Apr 2018}
  {
    \begin{cvitems}
    \item Worked on a web application using the MERN stack.
    \item Rewrote the entire nodejs server in typescript with unit testing in
      jasmine for better type-checking and code reliability.
    \item Also rewrote react app into an NgRx based angular app for better code
      organization and structure.
    \item Technologies Used: MongoDB, React, NodeJS, Angular
    \end{cvitems}
  }
  \fi

\end{cventries}

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv.tex"
%%% End: